Model of lens candidates from Space Warps CFHTLS

### 2016-07-26 paper2.tex
more detaiols on subsampling

\newcommand{\Mstel}{M_{\rm stel}}
\newcommand{\Mhalo}{M_{\rm h}}
\newcommand{\haloindex}{\mathcal{H}}

@@

Recent searches through the CFHTLS \citep{2012SPIE.8448E..0MC} using
arc-finders
\citep{2012ApJ...749...38M,2014A&A...567A.111M,2014ApJ...785..144G} by
machine learning \citep{2016arXiv160504309P} and by visual inspection
by a citizen-science volunteers
\citep[Space~Warps][]{2016MNRAS.455.1191M} have between them
discovered an average of four lenses per square degree.  So one can be
optimistic about finding many thousands of lenses in the next
generation of wide-field surveys.  The expected flood of new lens
discoveries will need a similarly huge modelling modelling effort to
reconstruct their mass distributions.  To prepare for the challenge of
massive-sample lens modelling, \cite{2015MNRAS.447.2170K} developed a
new modelling strategy, implemented as the SpaghettiLens system.  The
idea is to collaborate with experienced members of the citizen-science
community, who have already participated in lens discovery through
Space~Warps, as well as several other projects involving astronomical
data.  In this paper, we present SpaghettiLens models of
lens-candidates discovered through Space~Warps.

@@

A modeller's main input to SpaghettiLens is a sketch of arrival-time
contours on a lensed system.  It gives the locations (or best-guess
locations) of images of point-like sources, along with their ordering
in arrival time, and their parities (minumum, saddle-point or
maximum).  Such a sketch, which we call a spaghetti diagram, tends to
resemble the form of lensed arcs, but it also in effect encodes
encodes a proposal for its mass distribution.  A spaghetti diagram is
read by a server-side numerical engine \citep[GLASS, developed
  by][]{2014MNRAS.445.2181C} which then returns a statistical ensemble
of mass maps.  The mass maps are made up of mass tiles and are
free-form, except that they are required to be concentrated around the
identified lens centre.  They are also required to reproduce the given
image locations, parities and time ordering exactly.  Graphical
representations of the mass map and arrival-time surface are returned
to the user for review.  The user can post these results on a forum,
or discard them and try again.  Volunteers can start the modelling
process afresh, or they can take an existing model from the forum and
modify its input spaghetti diagram or its accompanying options, and
thus obtain a revised model.

@@

\begin{figure}
  \includegraphics[width=.9\linewidth]{img/hires_comparison/ASW000102p_6941_11_hires_comparison}
  \includegraphics[width=.9\linewidth]{img/hires_comparison/ASW000102p_6941_13_hires_comparison}
  \includegraphics[width=.9\linewidth]{img/hires_comparison/ASW000102p_6941_33_hires_comparison}
  \caption{Model improvement resulting from using smaller mass tiles
    in the inner region of the mass model.  Shown here are the average
    enclosed $\kappa$ within a given projected radius, for three
    different reconstructions of a simulated lens (sim) from
    Space~Warps.  In each panel, the dashed blue curve is the correct
    answer.  The orange band represents the statistical ensemble from
    SpaghettiLens, the red line being the ensemble mean.  Locations of
    images (maximum, saddle point, minimum) are marked with vertical
    arrows.  Crossing the horizontal $\kappa=1$ line is the effective
    Einstein radius, and is so labelled. The upper panel is from
    K\"ung et al., (2015) (see Figure~3 of that paper).  The middle
    panel is the result when the innermost mass tile is replaced by 9
    smaller tiles.  The lower panel results from replacing each of the
    innermost 9 tiles each with 9 smaller tiles.}
  \label{fig:subsampling}
\end{figure}

@@

Figure~\figref{subsampling} shows an experiment with smaller mass
tiles in the inner region.  Replacing the very central mass tile with
9 smaller tiles allows for steeper central profiles.  Doing the same
for the 21 innermost mass tiles \todo{Check meaning of hires
  parameters.} solves the problem completely, but doubles the
computation time.  The main modelling work in this paper was, however,
done before the experiments with smaller mass tiles was complete.
Hence the results in this paper use the intermediate option
(corresponding to the middle panel in Figure~\figref{subsampling}).
As the results in this paper mainly concern the enclosed mass in the
outer regions, the remaining shallowness in the central region should
be inconsequential.

@@

\begin{enumerate}
\item In the upper row we have first a cutout of the Space~Warps
  image, marked up with a spaghetti diagram.  There are four distinct
  lensed images, and the spaghetti diagram proposes that they are a
  minimum nearest to the lensing galaxy, a close minimum-saddle pair,
  and a minimum further away. In Table~\ref{tab:models} we refer to
  such configurations as IQ for inclined quad.
\item Alongside is a synthetic image produced by modelling.  In it,
  the fitted lensed images are shown in colour, while the lensing
  galaxy and extraneous objects have been reduced to grayscale.
  (Figure~\figref{synthimg} in \S~\ref{subsec:sourcefit} shows a
  synthetic image from another model of the same system.) These two
  panels are qualitative and display no units, and moreover, the
  mutual alignment of the two panels is only approximate.
\item The middle row shows contour maps from the model.  At middle
  left, we have the arrival-time surface.
\item At middle right we have the mass distribution in the usual
  dimensionless form $\kappa$.  Again, these two panels are mainly
  qualitative: both panels are spatially registered and centred on the
  density-peak of the lens, but no scales have been included.
\item The base row supplies spatial and mass scales.  The left panel
  shows the circularly-averaged $\kappa$ of the model ensemble, with
  increasing radius (in arcsec).  The four short vertical lines
  correspond to the minima and saddle points marked in the upper-left
  panel.  The effective Einstein radius is also shown.  As the radius
  scale indicates SW05 is comparatively large lens on the
  sky.
\item Lower right shows the total mass in the model against the
  estimated stellar mass, alongside the values for the whole sample.
  The lower-right shaded region is unphysical according to the
  stellar-population models, because it gives $M<\Mstel$. The
  upper-left shaded region is unphysical according to abundance
  matching, because it gives $M>\Mhalo$.  That is to say, the unshaded
  region is $0<\haloindex<1$.
\end{enumerate}

>>>>

\newcommand{\Mstel}{M_{\rm stel}}
\newcommand{\Mhalo}{M_{\rm h}}
\newcommand{\haloindex}{\mathcal{H}}
\newcommand{\ER}{$\Theta_{\text{E}}$} % einstein radius

@@

Recent searches through the CFHTLS \citep{2012SPIE.8448E..0MC} using
arc-finders
\citep{2012ApJ...749...38M,2014A&A...567A.111M,2014ApJ...785..144G} by
machine learning \citep{2016arXiv160504309P} and by visual inspection
by a citizen-science volunteers
\citep[Space~Warps][]{2016MNRAS.455.1191M} have between them
discovered an average of four lenses per square degree.  So one can be
optimistic about finding many thousands of lenses in the next
generation of wide-field surveys.  The expected flood of new lens
discoveries will need a similarly huge modelling effort to
reconstruct their mass distributions.  To prepare for the challenge of
massive-sample lens modelling, \cite{2015MNRAS.447.2170K} developed a
new modelling strategy, implemented as the SpaghettiLens system.  The
idea is to collaborate with experienced members of the citizen-science
community, who have already participated in lens discovery through
Space~Warps, as well as several other projects involving astronomical
data.  In this paper, we present SpaghettiLens models of
lens-candidates discovered through Space~Warps.

@@

A modeller's main input to SpaghettiLens is a sketch of arrival-time
contours on a lensed system.  It gives the locations (or best-guess
locations) of images of point-like sources, along with their ordering
in arrival time, and their parities (minumum, saddle-point or
maximum).  Such a sketch, which we call a spaghetti diagram, tends to
resemble the form of lensed arcs, but it also in effect 
encodes a proposal for its mass distribution.  A spaghetti diagram is
read by a server-side numerical engine \citep[GLASS, developed
  by][]{2014MNRAS.445.2181C} which then returns a statistical ensemble
of mass maps.  The mass maps are made up of mass tiles and are
free-form, except that they are required to be concentrated around the
identified lens centre.  They are also required to reproduce the given
image locations, parities and time ordering exactly.  Graphical
representations of the mass map and arrival-time surface are returned
to the user for review.  The user can post these results on a forum,
or discard them and try again.  Volunteers can start the modelling
process afresh, or they can take an existing model from the forum and
modify its input spaghetti diagram or its accompanying options, and
thus obtain a revised model.

@@

\begin{figure}
  \includegraphics[width=.9\linewidth]{img/hires_comparison/ASW000102p_6941_11_hires_comparison}
  \includegraphics[width=.9\linewidth]{img/hires_comparison/ASW000102p_6941_13_hires_comparison}
  \includegraphics[width=.9\linewidth]{img/hires_comparison/ASW000102p_6941_33_hires_comparison}
  \caption{Model improvement resulting from using smaller mass tiles
    in the inner region of the mass model.  Shown here are the average
    enclosed $\kappa$ within a given projected radius, for three
    different reconstructions of a simulated lens (sim) from
    Space~Warps.  In each panel, the dashed blue curve is the correct
    answer.  The orange band represents the statistical ensemble from
    SpaghettiLens, the orange line being the ensemble mean.  Locations of
    images (maximum, saddle point, minimum) are marked with vertical
    arrows.  Crossing the horizontal $\kappa=1$ line is the effective
    Einstein radius \ER, and is so labelled. The upper panel is from
    K\"ung et al., (2015) (see Figure~3 of that paper).  The middle
    panel is the result when the innermost mass tile is replaced by 9
    smaller tiles.  The lower panel results from replacing each of the
    innermost 5 by 5 tiles each with 9 smaller tiles.}
  \label{fig:subsampling}
\end{figure}

@@

Figure~\figref{subsampling} shows an experiment with smaller mass
tiles in the inner region.  Replacing the very central mass tile with
9 smaller tiles allows for steeper central profiles.  Doing the same
for the 25 innermost mass tiles solves the problem completely, but increases
the number of mass tiles by 40% and thus at least triples the
% in practice, it's more x4 - x5! 87/22, 86/21, 85/16
computation time.  The main modelling work in this paper was, however,
done before the experiments with smaller mass tiles was complete.
Hence the results in this paper use the intermediate option
(corresponding to the middle panel in Figure~\figref{subsampling}).
As the results in this paper mainly concern the enclosed mass in the
outer regions, the remaining shallowness in the central region should
be inconsequential.

@@

\begin{enumerate}
\item In the upper row we have first a cutout of the Space~Warps
  image, marked up with a spaghetti diagram.  There are four distinct
  lensed images, and the spaghetti diagram proposes that they are a
  minimum nearest to the lensing galaxy, a close minimum-saddle pair,
  and a minimum further away. In Table~\ref{tab:models} we refer to
  such configurations as IQ for inclined quad.
\item Alongside is a synthetic image produced by modelling.  In it,
  the fitted lensed images are shown in colour, while the lensing
  galaxy and extraneous objects have been reduced to grayscale.
  (Figure~\figref{synthimg} in \S~\ref{subsec:sourcefit} shows a
  synthetic image from another model of the same system.) These two
  panels are qualitative and display no units, and moreover, the
  mutual alignment of the two panels is only approximate.
\item The middle row shows contour maps from the model.  At middle
  left, we have the arrival-time surface.
\item At middle right we have the mass distribution in the usual
  dimensionless form $\kappa$.  Again, these two panels are mainly
  qualitative: both panels are spatially registered and centred on the
  density-peak of the lens, but no scales have been included.
\item The base row supplies spatial and mass scales.  The left panel
  shows the circularly-averaged $\kappa$ of the model ensemble, with
  increasing radius (in arcsec).  The four short vertical lines
  correspond to the minima and saddle points marked in the upper-left
  panel.  The effective Einstein radius \ER is also shown.  As the radius
  scale indicates SW05 is comparatively large lens on the
  sky.
\item Lower right shows the total mass in the model against the
  estimated stellar mass, alongside the values for the whole sample.
  The lower-right shaded region is unphysical according to the
  stellar-population models, because it gives $M<\Mstel$. The
  upper-left shaded region is unphysical according to abundance
  matching, because it gives $M>\Mhalo$.  That is to say, the unshaded
  region is $0<\haloindex<1$.
\end{enumerate}
